partial: An R Package for Creating Partial Dependence Plots

### 2016-09-01 manuscript/greenwell.tex
commented out example summary

In this paper, we showed how to construct PDPs for various types of black box models in R using the \pkg{partial} package. We also briefly discussed related approaches availble in other R packages as well. Suggestions to avoid extrpolation and high excecution times were discussed and demonstrated via examples. There is a bright future for \pkg{partial} in terms of growth. For example, it would be useful to have the ability to construct PDPs for black box survival models---like conditional random forests with censored response---and \CRANpkg{xgboost} \citep{xgboost-pkg} models.

>>>>

In this paper, we showed how to construct PDPs for various types of black box models in R using the \pkg{partial} package. We also briefly discussed related approaches availble in other R packages as well. Suggestions to avoid extrpolation and high excecution times were discussed and demonstrated via examples. There is a bright future for \pkg{partial} in terms of growth. For example, it would be useful to have the ability to construct PDPs for black box survival models---like conditional random forests with censored response. % We introduced the investr package for computing point estimates along with inversion and Waldbased confidence intervals for linear and nonlinear calibration problems with constant variance. We also showed how the boot package can be used for constructing approximate 100(1 􀀀 a)% calibration intervals, which for convenience, may be incorporated into a future release of investr. The authors are currently working on extending the package to handle the case of heteroscedastic errors, random coefficient models (e.g., objects of class "lme" from the recommended nlme package; Pinheiro et al., 2014)), and even multivariate calibration problems (e.g., objects of class "mlm").
